<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Fisher test simulation}
-->

`https://github.com/clMathLibraries/clRNG`


## Fisher test simulation
```{r packages, results='hide'}
library('gpuR')
library("clrng")
```

```{r memoryAvailable, echo=TRUE, results='hide'}
gpuInfo()$deviceName   #gpuInfo()$maxAllocatableMem/(1024^3)
```


#Fisher simulation example
This table is small in dimension and size of values, doesn't need a simulation. We still do the simulation on GPU just for demonstration and test.
See more tests on real data examples on section 4 of paper "Ruoyong Xu, Patrick Brown, Pierre L’Ecuyer (2021). A tool set for random number generation on GPUs in R."
```{r  teaTasting, eval=F}
TeaTasting <-matrix(c(3, 1, 1, 3),nrow=2)
TeaTasting

## Using the R function 
fisher.test(TeaTasting)$p.value
## 0.4857143


## Using GPU
TeaTasting<-vclMatrix(TeaTasting,type="integer")
streams <-  gpuR::vclMatrix(clrng::createStreamsCpu(n=64*16))
result<-clrng::fisher.sim(TeaTasting, N=100000L, streams=streams, returnStatistics=TRUE, type="double", Nglobal=c(16,64))
result$counts
result$p.value
result$threshold
result$simNum
result$streams
result$sim
as.vector(result$sim)[10:20]
length(result$sim)
```



streams <-  gpuR::vclMatrix(clrng::createStreamsCpu(n=64*16))
typeof(streams)
result2<-clrng::fisher.sim(TeaTasting, 100000L, streams=streams,returnStatistics=F, type="double", Nglobal=c(16,64))
result2$p.value
t(as.matrix(streams))[,5:8]

result2$simNum
result2$counts









